Simulataneous Robot Localization and \\Environment Mapping with \\Simulated Sensor Measurements

### 2018-05-03 paper.tex
almost done?

\author{Swapnil~Pande
        and~Joshua~Petrin,
        ~\IEEEmembership{EECE~3892-04,~Dr.~Richard~Alan~Peters}% <-this % stops a space
\thanks{M. Shell was with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

@@

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/playing-field.jpg}
\caption{Diagram of competition field \cite{nasa-rmc-rules}}
\label{fig:playing-field}
\end{figure}

@@

@@

The motion model update for the \textit{a priori} estimate is defined with the following relation, given
the robot's control sequence straight-line velocity $v_t$ and angular velocity $\omega_t$:
\begin{equation*}
\left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           x_{t+1} \\
           y_{t+1} \\
           \theta_{t+1}
           \end{IEEEeqnarraybox*}\right] = 
           \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           x_{t} \\
           y_{t} \\
           \theta_{t}
           \end{IEEEeqnarraybox*}\right] + 
           \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           -v_t/\omega_t \sin(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t)\\
           v_t/\omega_t \cos(\theta_t) - v_t/\omega_t\cos(\theta_t + \omega_t \Delta t)\\
           \omega_t \Delta t
           \end{IEEEeqnarraybox*}\right]
\end{equation*}
If covariance of the current state is $\Sigma_t$, then the Extended Kalman Filter approximates the 
covariance of the new \textit{a priori} state $\widehat{\Sigma_{t}}$ to be 
\begin{equation*}
 \widehat{\Sigma_t} = G_t \Sigma_t G_t^T + R_t,
\end{equation*}
where $G_t$ is the Jacobian of the robot's motion, and $R_t$ is a noise factor. Formally,
\begin{equation*}
G_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c/c,}
            G^x_t & \textbf{0} \\
            \textbf{0} & I_{2N \times 2N}
           \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $N$ is the number of obstacles (the quantity $2N$ above is because there are two coordinates for
each obstacle) and
\begin{equation*}
 G^x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c/c/c,}
            1\,   &  \, 0 \,  &  -v_t/\omega_t \cos(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t) \\
            0\,   &  \, 1 \,  &  -v_t/\omega_t \sin(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t) \\
            0\,   &  \, 0 \,  &   1
           \end{IEEEeqnarraybox*}\right].
\end{equation*}

@@

The Kalman gain is a weight for the updated state and covariance to depend on the predicted state 
verses the observed state. The updated state is
\begin{equation*}
 x_{t+1} = \hat{x_t} + K_t(z_t-h(\hat{x_t})),
\end{equation*}
and the updated covariance is 
\begin{equation*}
 \Sigma_{t+1} = (I - K_t H_t) \widehat{\Sigma_t}.
\end{equation*}
This \textit{a posteriori} correction step is performed for each set of sensor data to get an accurate
value for the mean and covariance of the new state.

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

>>>>

\author{Swapnil~Pande
        and~Joshua~Petrin,
        ~\IEEEmembership{EECE~3892-04,~Dr.~Richard~Alan~Peters}% <-this % stops a space
%\thanks{M. Shell was with the Department
%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}

@@

% Note that keywords are not normally used for peerreview papers.
%\begin{IEEEkeywords}
%IEEE, IEEEtran, journal, \LaTeX, paper, template.
%\end{IEEEkeywords}

@@

@@

\begin{figure*}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/playing-field.png}
\caption{Diagram of competition field \cite{nasa-rmc-rules}}
\label{fig:playing-field}
\end{figure*}

@@

The motion model update for the \textit{a priori} estimate is defined with the following relation, given
the robot's control sequence straight-line velocity $v_t$ and angular velocity $\omega_t$:
\begin{equation*}
\left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           x_{t+1} \\
           y_{t+1} \\
           \theta_{t+1}
           \end{IEEEeqnarraybox*}\right] = 
           \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           x_{t} \\
           y_{t} \\
           \theta_{t}
           \end{IEEEeqnarraybox*}\right] + 
           \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           -v_t/\omega_t \sin(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t)\\
           v_t/\omega_t \cos(\theta_t) - v_t/\omega_t\cos(\theta_t + \omega_t \Delta t)\\
           \omega_t \Delta t
           \end{IEEEeqnarraybox*}\right]
\end{equation*}
If covariance of the current state is $\Sigma_t$, then the Extended Kalman Filter approximates the 
covariance of the new \textit{a priori} state $\widehat{\Sigma_{t}}$ to be 
\begin{equation*}
 \widehat{\Sigma_t} = G_t \Sigma_t G_t^T + R_t,
\end{equation*}
where $G_t$ is the Jacobian of the robot's motion, and $R_t$ is a noise factor \cite{prob-robots}. Formally,
\begin{equation*}
G_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c/c,}
            G^x_t & \textbf{0} \\
            \textbf{0} & I_{2N \times 2N}
           \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $N$ is the number of obstacles (the quantity $2N$ above is because there are two coordinates for
each obstacle) and
\begin{equation*}
 G^x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c/c/c,}
            1\,   &  \, 0 \,  &  -v_t/\omega_t \cos(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t) \\
            0\,   &  \, 1 \,  &  -v_t/\omega_t \sin(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t) \\
            0\,   &  \, 0 \,  &   1
           \end{IEEEeqnarraybox*}\right].
\end{equation*}

@@

The Kalman gain is a weight for the updated state and covariance to depend on the predicted state 
verses the observed state. The updated state is
\begin{equation*}
 x_{t+1} = \hat{x_t} + K_t(z_t-h(\hat{x_t})),
\end{equation*}
and the updated covariance is 
\begin{equation*}
 \Sigma_{t+1} = (I - K_t H_t) \widehat{\Sigma_t}.
\end{equation*}
This \textit{a posteriori} correction step is performed for each set of sensor data to get an accurate
value for the mean and covariance of the new state. \cite{prob-robots}

\section{Experimental Results}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/1-actual-predicted-error-x.jpg}
\caption{}
\label{fig:1}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/2-actual-predicted-error-y.jpg}
\caption{}
\label{fig:2}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/3-actual-predicted-error-theta.jpg}
\caption{}
\label{fig:3}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/4-pred-state-var-x.jpg}
\caption{}
\label{fig:4}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/5-pred-state-var-y.jpg}
\caption{}
\label{fig:5}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/6-pred-state-var-theta.jpg}
\caption{}
\label{fig:6}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/7-landmarks-over-time.jpg}
\caption{}
\label{fig:7}
\end{figure}

\section{Discussion}

@@

\appendices

@@

% use section* for acknowledgment
